Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi

### 2011-12-19 ms.tex
Edit with a lot of MVs comments incorporated

Given the upper limit on the observed gamma-ray rate,
$R_{\gamma}(99\%\ \mathrm{CL}) = N_{\gamma}(99\%\ \mathrm{CL}) / T_{\mathrm{obs}}$, we can place
constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$. Integrating Eq.
(\ref{eqn:WIMPflux}) over energy we find
\begin{equation}
\expval{\sigma v}(99\%\ \mathrm{CL}) <
R_{\gamma}(99\%\ \mathrm{CL})\, \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}\,
\frac{1}{\int^{m_{\chi}}_{0} dE\ A_{\mathrm{eff}}\,N_\gamma (E)},
\end{equation}
where $A_{\mathrm{eff}}$ is the effective area of the gamma-ray detector.
Because the self-annihilation of a WIMP is a two-body process, the astrophysical factor
$J(\Delta\Omega)$ is the line-of-sight integral of the DM density squared
\begin{equation}
J(\Delta\Omega)=\int_{\Delta\Omega}d\Omega\int d\lambda\ \rho_{\chi}(\lambda)^{2}(\lambda,\Omega),
\end{equation}
where $\lambda$ represents the line-of-sight. In this work, we have modeled the Coma DM
distribution with a Navarro, Frenk and White (NFW) profile,
\citet{article:NavarroFrenkWhite:1997},
\begin{equation}
\rho_{\chi}(r)=\rho_{s}\left(\frac{r}{r_{s}}\right)^{-1}\left(1+\frac{r}{r_{s}}\right)^{-2},
\end{equation}
where $r_{s}$ is the scale radius and $\rho_{s}$ isthe scale density. Using weak weak-lensing
measurements of the virial mass in the Coma cluster \citep{article:Gavazzi_etal:2009} and the DM
halo mass-concentration relation derived from N-body simulation of structure formation 
\citep{article:Bullock_etal:2001}, we find for these parameters $r_{s}=0.654$ Mpc and
$\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. Table \ref{table:astrofactor} lists the
astrophysical factors calculated for the different VERITAS apertures considered in this work.
It also lists the astrophysical factor calculated for the background region, which is used
to estimate the gamma-ray contamination due to DM in the background region.

>>>>

Given the upper limit on the observed gamma-ray rate,
$R_{\gamma}(99\%\ \mathrm{CL}) = N_{\gamma}(99\%\ \mathrm{CL}) / T_{\mathrm{obs}}$, we can place
constraints on the WIMP parameter space $(m_{\chi}, \expval{\sigma v})$. Integrating Eq.
(\ref{eqn:WIMPflux}) over energy we find
\begin{equation}
\expval{\sigma v}(99\%\ \mathrm{CL}) <
R_{\gamma}(99\%\ \mathrm{CL})\, \frac{8\pi m_{\chi}^{2}}{J(\Delta\Omega)}\,
\frac{1}{\int^{m_{\chi}}_{0} dE\ A_{\mathrm{eff}}\,N_\gamma (E)},
\end{equation}
where $A_{\mathrm{eff}}$ is the effective area of the gamma-ray detector.
Because the self-annihilation of a WIMP is a two-body process, the astrophysical factor
$J(\Delta\Omega)$ is the line-of-sight integral of the DM density squared
\begin{equation}
J(\Delta\Omega)=\int_{\Delta\Omega}d\Omega\int d\lambda\ \rho_{\chi}(\lambda)^{2}(\lambda,\Omega),
\end{equation}
where $\lambda$ represents the line-of-sight. In this work, we have modeled the Coma DM
distribution with a Navarro, Frenk and White (NFW) profile,
\citet{article:NavarroFrenkWhite:1997},
\begin{equation}
\rho_{\chi}(r)=\rho_{s}\left(\frac{r}{r_{s}}\right)^{-1}\left(1+\frac{r}{r_{s}}\right)^{-2},
\end{equation}
where $r_{s}$ is the scale radius and $\rho_{s}$ isthe scale density. Using weak weak-lensing
measurements of the virial mass in the Coma cluster \citep{article:Gavazzi_etal:2009} and the DM
halo mass-concentration relation derived from N-body simulation of structure formation 
\citep{article:Bullock_etal:2001}, we find for these parameters $r_{s}=0.654$ Mpc and
$\rho_{s}=4.4\times 10^{4}$ M$_{\odot}$/Mpc$^{3}$. Table \ref{table:astrofactor} lists the
astrophysical factors calculated for the different VERITAS apertures considered in this work.
It also lists the astrophysical factor calculated for the background region, which is used
to estimate the gamma-ray contamination from DM annihilation in the background region.
